DRAFT: Towards a paper on patient movement in the Victorian hospital system

### 2025-04-02 reports/report.qmd
Update report
Some small updates

Understanding of the spread of AMR through hospital systems has been studied in the past as a network phenomenon. The movement of patients through the hospital systems induced by referrals can be represented as edges between hospital nodes. However, these networks are usually presented as static, where movement over a large period of time has been aggregated to form a single network. It is known, especially in other applications, that temporal networks can display different behaviour than the static equivalents. In this paper, we investigate these differences using the Victorian hospital system as a baseline for comparison. In particular, we investigate the impacts of the inclusion of modelling the period of time that patients spend at home between admissions, and the effect of approximating the granularity of the temporality]]]]].

@@

@@

::: {#new-eq}

>>>>

Understanding of the spread of AMR through hospital systems has been studied in the past as a network phenomenon [@donker_patient_2010]. 
The movement of patients through the hospital systems induced by referrals can be represented as edges between hospital nodes. 
However, these networks are usually presented as static, where movement over a large period of time has been aggregated to form a single network. 
It is known, especially in other applications, that temporal networks can display different behaviour than the static equivalents. 
In this paper, we investigate these differences using the Victorian hospital system as a baseline for comparison. 
In particular, we investigate the impacts of the inclusion of modelling the period of time that patients spend at home between admissions, and the effect of approximating the granularity of the temporality]]]]].

@@

Existing studies treating hospital systems as networks

@@

### 2025-04-02 reports/sketch.qmd
Some small updates

---
title: "DRAFT: Towards a paper on patient movement in the Victorian hospital system"
subtitle: "an exercise in trying to avoid reality"
author: "X-- xXx THE AUTHORS xXx --X"
filters:
  - tikz 
format: html
execute:
  echo: false
---

@@

```{python}
#| label: fig-ecdf
#| fig-cap: Empirical cumulative distributions of the observed hitting times to hospitals, where a single hospital is seeded with 30 tracked individuals. A plot of CDF of the analytical expected hitting times is also shown for the naïve static network model.
plt.figure()
for model, dist in hitting_time_dists.items():
    plt.plot(dist, np.linspace(0, 1, len(dist), endpoint=False), label=model)

@@

sns.despine()
```

@@

sns.despine()
```

@@

First we will examine why the static network yields faster spread than the series of static snapshots.
We propose that this is caused by the delay in connectedness of the snapshot network model.
```{python}
NO_CACHE = False 
connectedness_file = root / "outputs/snapshot_movement_analysis/overlay_connectedness.parquet"

@@

```{python}

S = ig.Graph.Read(root / "data/concordant_networks/trimmed_static_base_1_threshold_4.graphml")

@@

```{python}
deviations = (
  joined_table
  .filter(pl.col('dep_rate') > 0.0)
  .with_columns(
    deviation = pl.col('ss_indirect_rate') - pl.col('dep_rate')
  )
)

>>>>

---
title: 'DRAFT: Towards a paper on patient movement in the Victorian hospital system'
subtitle: an exercise in trying to avoid reality
author: X-- xXx THE AUTHORS xXx --X
filters:
  - tikz
format: html
execute:
  echo: false
jupyter:
  jupytext:
    text_representation:
      extension: .qmd
      format_name: quarto
      format_version: '1.0'
      jupytext_version: 1.16.4
  kernelspec:
    display_name: Python 3 (ipykernel)
    language: python
    name: python3
---

@@

```{python}
#| label: fig-ecdf
#| fig-cap: 'Empirical cumulative distributions of the observed hitting times to hospitals, where a single hospital is seeded with 30 tracked individuals. A plot of CDF of the analytical expected hitting times is also shown for the naïve static network model.'
plt.figure()
for model, dist in hitting_time_dists.items():
    plt.plot(dist, np.linspace(0, 1, len(dist), endpoint=False), label=model)

@@

sns.despine()

```

@@

sns.despine()

plt.savefig("early_time_ecdf.png", dpi=360)
```

@@

First we will examine why the static network yields faster spread than the series of static snapshots.
We propose that this is caused by the delay in connectedness of the snapshot network model.

```{python}
NO_CACHE = False 
connectedness_file = root / "outputs/snapshot_movement_analysis/overlay_connectedness.parquet"

@@

```{python}
S = ig.Graph.Read(root / "data/concordant_networks/trimmed_static_base_1_threshold_4.graphml")

@@

```{python}
#| label: fig-deviations-snapshot-vs-static
#| fig-cap: Deviation between indirect transfer rate of the static (mean) vs snapshot (time-varying) networks.
deviations = (
  joined_table
  .filter(pl.col('dep_rate') > 0.0)
  .with_columns(
    deviation = pl.col('ss_indirect_rate') - pl.col('dep_rate')
  )
)
